---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cherryr

<!-- badges: start -->
<!-- badges: end -->

The goal of cherryr is to simulate a game of Hi Ho Cherry-o. They will call the `play_game` function with arguments of the number of cherries to start with on the tree, and a max number of turns to allow the game to play. `play_game` will return a cherry object which contains information about the game including what happened on each turn. 

## Installation

You can install the development version of cherryr from [GitHub](https://github.com/) with:

``` r 
# install.packages("devtools")
devtools::install_github("wilsondmw/cherryr")
```

## Example

In order to simulate a game of Hi ho cherry O the user will call the 'play_game' function and specify the number of cherries that will start on the tree. 
```{r example}
devtools::load_all()
library(cherryr)
my_game <- play_game(10)
```

The above will return an object of the cherry class. It will primarily give the number of turns that it took to play a complete game, but the object will also store the results of each turn until the game is over which can be visulaised by calling the 'plot' function on a cherry object which will show cherries being removed from and added to the tree until the game is over.

```{r plot}
plot(my_game)
```

